Plot responses to model covariates to inform threshold choices for VOCC

### 2019-09-10 analysis/VOCC/3-fixed-var-response-plots.Rmd
add more species

# # Species run so far...
 species <- "Arrowtooth Flounder" # running more models

@@

 species <- "Walleye Pollock" # running more models
# species <- "Pacific Cod"
# species <- "Pacific Ocean Perch" # beautiful curves, no depth change

# species <- "Silvergray Rockfish" # beautiful curves, no depth change
 species <- "Quillback Rockfish" # overall a bit flat... running survey specific models
# species <- "Yelloweye Rockfish" # beautiful curves, with depth change
 species <- "Bocaccio" # good curves, no depth change ... should run survey specific models
 species <- "Sharpchin Rockfish"
# species <- "Splitnose Rockfish"
# species <- "Canary Rockfish"
# species <- "Rougheye/Blackspotted Rockfish Complex"
# species <- "Redbanded Rockfish"
# species <- "Greenstriped Rockfish"

# species <- "Longspine Thornyhead"
# species <- "Shortspine Thornyhead",
# species <- "Sablefish"
# species <- "Lingcod"

# species <- "North Pacific Spiny Dogfish" # note: using all data for maturity thresholds
# species <- "Longnose Skate"
#  species <- "Spotted Ratfish"
```

Choose model details
```{r}
covariates <- ""
# covariates <- "+muddy+mixed+rocky"
# covariates <- "+mixed+rocky"
#covariates <- "+muddy+any_rock"
# covariates <- "+trawled+muddy+rocky+mixed"
# covariates <- "+trawled+mixed+rocky"
# covariates <- "+trawled+mixed"

# priors <- FALSE
# covariates <- "+muddy+any_rock"
# covs <- gsub("\\+", "-", covariates)
priors <- TRUE
#covs <- "-tv-depth"
covs <- "-both-tv-depth"
num_params <- 2
```

@@

  if (length(do[[i]])>0) {
   do[[i]]$species <- species
   do[[i]]$age <- ifelse(grepl("imm", names(model_list[i])), "imm", "adult")
   do[[i]]$model <- names(model_list[i])
   do[[i]]$covs <- covs 
   roots <- get_quadratic_roots(model_list[[i]], predictor = "do_mlpl", fixed_param = 1, threshold = 0.5)
   do[[i]]$optimal_do <- roots[["optimal"]]
   do[[i]]$lower_do_50 <- roots[["lower_threshold"]]
   do[[i]]$upper_do_50 <- roots[["upper_threshold"]]
   roots75 <- get_quadratic_roots(model_list[[i]], predictor = "do_mlpl", fixed_param = 1, threshold = 0.75)
   do[[i]]$lower_do_75 <- roots75[["lower_threshold"]]
   do[[i]]$upper_do_75 <- roots75[["upper_threshold"]]
   roots25 <- get_quadratic_roots(model_list[[i]], predictor = "do_mlpl", fixed_param = 1, threshold = 0.25)
   do[[i]]$lower_do_25 <- roots25[["lower_threshold"]]
   do[[i]]$upper_do_25 <- roots25[["upper_threshold"]]
   do_plots[[i]] <- 
     plot_mountains(do[[i]], variable_label = "Dissolved O2", xlimits = c(0, 8)) +
        ggtitle(paste(species, names(model_list[i]))) +
        geom_vline(xintercept=do[[i]]$optimal_do, size= 1.2, colour = "darkgrey") + 
        geom_vline(xintercept=do[[i]]$lower_do_50, linetype="longdash", alpha = 0.75) + 
        geom_vline(xintercept=do[[i]]$upper_do_50, linetype="longdash", alpha = 0.75) +
        geom_vline(xintercept=do[[i]]$lower_do_75, linetype="dotted", alpha = 0.5) + 
        geom_vline(xintercept=do[[i]]$upper_do_75, linetype="dotted", alpha = 0.5) +
        geom_vline(xintercept=do[[i]]$lower_do_25, linetype="dotted", alpha = 0.5) + 
        geom_vline(xintercept=do[[i]]$upper_do_25, linetype="dotted", alpha = 0.5) 
   } else {
    do_plots[[i]] <- grid::grid.rect(gp = grid::gpar(col = "white"))
   }
 } else {
  do_plots[[i]] <- grid::grid.rect(gp = grid::gpar(col = "white"))
 }
}

@@

#### Calculate temperature curves
```{r}
td <- list()
temp_plots <- list()
for (i in seq_len(length(model_list))) {
 if(model_list[[i]]$model$convergence==0){
  td[[i]] <- fixed_density(model_list[[i]], predictor = "temp", fixed_params = num_params)
  if (length(td[[i]])>0) {
    td[[i]]$species <- species
    td[[i]]$age <- ifelse(grepl("imm", names(model_list[i])), "imm", "adult")
    td[[i]]$model <- names(model_list[i])
    td[[i]]$covs <- covs
   roots <- get_quadratic_roots(model_list[[i]], predictor = "temp", fixed_param = num_params, threshold = 0.5)
   td[[i]]$optimal_temp <- roots[["optimal"]]
   td[[i]]$lower_t_50 <- roots[["lower_threshold"]]
   td[[i]]$upper_t_50 <- roots[["upper_threshold"]]
   roots75 <- get_quadratic_roots(model_list[[i]], predictor = "temp", fixed_param = num_params, threshold = 0.75)
   td[[i]]$lower_t_75 <- roots75[["lower_threshold"]]
   td[[i]]$upper_t_75 <- roots75[["upper_threshold"]]
   roots25 <- get_quadratic_roots(model_list[[i]], predictor = "temp", fixed_param = num_params, threshold = 0.25)
   td[[i]]$lower_t_25 <- roots25[["lower_threshold"]]
   td[[i]]$upper_t_25 <- roots25[["upper_threshold"]]
   temp_plots[[i]] <- 
     plot_mountains(td[[i]], variable_label = "Temperature", xlimits = c(2, 10)) +
        ggtitle(paste(species, names(model_list[i]))) +
        geom_vline(xintercept=td[[i]]$optimal_t, size= 1.2, colour = "darkgrey") + 
        geom_vline(xintercept=td[[i]]$lower_t_50, linetype="longdash", alpha = 0.75) + 
        geom_vline(xintercept=td[[i]]$upper_t_50, linetype="longdash", alpha = 0.75) +
        geom_vline(xintercept=td[[i]]$lower_t_75, linetype="dotted", alpha = 0.5) + 
        geom_vline(xintercept=td[[i]]$upper_t_75, linetype="dotted", alpha = 0.5) +
        geom_vline(xintercept=td[[i]]$lower_t_25, linetype="dotted", alpha = 0.5) + 
        geom_vline(xintercept=td[[i]]$upper_t_25, linetype="dotted", alpha = 0.5)

@@

Save DO plots
```{r}
png(
  file = paste0("figs/", spp, "/do-fixed-", spp, covs, "-priors-", priors, ".png"),
  res = 600,
  units = "in",
  width = 8.5,
  height = 11
)
gridExtra::grid.arrange(
  grobs = do_plots,
  ncol = 2,
  top = grid::textGrob(paste(species))
)
dev.off()
```

Save Temperature plots
```{r}
png(
  file = paste0("figs/", spp, "/temp-fixed-", spp, covs, "-priors-", priors, ".png"),
  res = 600,
  units = "in",
  width = 8.5,
  height = 11
)
gridExtra::grid.arrange(
  grobs = temp_plots,
  ncol = 2,
  top = grid::textGrob(paste(species))
)
dev.off()
```

#### Save plots of raw densities vs model optimals 
```{r}
png(
  file = paste0("figs/", spp, "/check-optimals-", spp, covs, "-priors-", priors, ".png"),
  res = 600,
  units = "in",
  width = 8.5,
  height = 11
)
gridExtra::grid.arrange(grobs = c(raw_do_plots, raw_t_plots),
  ncol = 2,
  top = grid::textGrob(paste("Raw densities of", species, "with modeled optimals in vertical lines (if solid includes all surveys)"))
)
dev.off()
```

#### Save plots of time-varying depth from climate model
```{r}
png(
  file = paste0(
    "figs/", spp,
    "/depth-", spp, covs, "-priors-", priors, ".png"
  ),
  res = 600,
  units = "in",
  width = 8.5,
  height = 11
)
gridExtra::grid.arrange(
  grobs = depth_plots,
  ncol = 2,
  top = grid::textGrob(paste(species))
)
dev.off()
```

>>>>

# # Species run so far...
# species <- "Arrowtooth Flounder" # temp good, not DO, imm moving deeper?

@@

# species <- "Walleye Pollock" # survey 4 or 16 might work
# species <- "Pacific Cod"

## Sebastes
# 
# ## TRY BOTH - not schooling
#  species <- "Yelloweye Rockfish" # beautiful curves, with depth change ***
#  species <- "Bocaccio" # good curves, no depth change ... most survey-specific models fail to find minimum ***
#  species <- "Sharpchin Rockfish" # beautiful curves, imm depth change ***
#  species <- "Greenstriped Rockfish" # beautiful curves for adults, no depth change ***

# ## TRY BOTH - schooling
#  species <- "Pacific Ocean Perch" # beautiful curves, no depth change, schooling ***
#  species <- "Silvergray Rockfish" # beautiful curves, no depth change, schooling ***

# ## TRY JUST TEMPERATURE 
# # species <- "Rougheye/Blackspotted Rockfish Complex" # good temp, not DO
# # species <- "Redbanded Rockfish" # good temp, not DO, maybe moving shallower
#  species <- "Splitnose Rockfish" # good temp, survey 4 DO ok

# # species <- "Yellowtail Rockfish" #  good temp for survey 4 only, no DO, schooling
# # species <- "Quillback Rockfish" # like warm = overall a bit flat... territorial! 
# # species <- "Canary Rockfish" # schooling, winter-birthing, and depth change!, but curves at edges... adult1 looks ok?
#  species <- "Widow Rockfish" # schooling, and depth change, but curves at edges

# species <- "Longspine Thornyhead" # too deep to produce curves
# species <- "Shortspine Thornyhead"
# species <- "Sablefish" # temp might work, no DO, no consistant depth change
# species <- "Lingcod" # curves ok, overall a bit flat
# # species <- "Pacific Hake" # not useful

# species <- "North Pacific Spiny Dogfish" # too flat, but with depth change! note: pooled maturity 
# species <- "Longnose Skate" # do too flat, temp from 4 might be useful, seems to go deeper?
# species <- "Big Skate"
# species <- "Sandpaper Skate"
# species <- "Brown Cat Shark"
# species <- "Spotted Ratfish" # curves not useful because to abundant in shallow
```

Choose model details
```{r}
covariates <- ""
# covariates <- "+muddy+mixed+rocky"
# covariates <- "+mixed+rocky"
#covariates <- "+muddy+any_rock"
# covariates <- "+trawled+muddy+rocky+mixed"
# covariates <- "+trawled+mixed+rocky"
# covariates <- "+trawled+mixed"
# 
# covariates <- "+as.factor(ssid)"
# covs <- "-both-tv-depth-ssid"

# priors <- FALSE
# covariates <- "+muddy+any_rock"
# covs <- gsub("\\+", "-", covariates)
priors <- TRUE
#covs <- "-tv-depth"
covs <- "-both-tv-depth"

num_params <- 2
```

@@

  if (length(do[[i]])>0) {
   do[[i]]$species <- species
   do[[i]]$age <- ifelse(grepl("imm", names(model_list[i])), "imm", "adult")
   do[[i]]$ssid <- unique(model_list[[i]]$data$ssid)
   do[[i]]$model <- names(model_list[i])
   do[[i]]$covs <- covs 
   roots <- get_quadratic_roots(model_list[[i]], predictor = "do_mlpl", fixed_param = 1, threshold = 0.5)
   do[[i]]$optimal_do <- roots[["optimal"]]
   do[[i]]$lower_do_50 <- roots[["lower_threshold"]]
   do[[i]]$upper_do_50 <- roots[["upper_threshold"]]
   roots75 <- get_quadratic_roots(model_list[[i]], predictor = "do_mlpl", fixed_param = 1, threshold = 0.75)
   do[[i]]$lower_do_75 <- roots75[["lower_threshold"]]
   do[[i]]$upper_do_75 <- roots75[["upper_threshold"]]
   roots25 <- get_quadratic_roots(model_list[[i]], predictor = "do_mlpl", fixed_param = 1, threshold = 0.25)
   do[[i]]$lower_do_25 <- roots25[["lower_threshold"]]
   do[[i]]$upper_do_25 <- roots25[["upper_threshold"]]
   do_plots[[i]] <- 
     plot_mountains(do[[i]], variable_label = "Dissolved O2", xlimits = c(0, 8)) +
        ggtitle(paste(species, names(model_list[i]))) +
        geom_vline(xintercept=do[[i]]$optimal_do, size= 1.2, colour = "darkgrey") + 
        geom_vline(xintercept=do[[i]]$lower_do_50, linetype="longdash", alpha = 0.75) + 
        geom_vline(xintercept=do[[i]]$upper_do_50, linetype="longdash", alpha = 0.75) +
        geom_vline(xintercept=do[[i]]$lower_do_75, linetype="dotted", alpha = 0.5) + 
        geom_vline(xintercept=do[[i]]$upper_do_75, linetype="dotted", alpha = 0.5) +
        geom_vline(xintercept=do[[i]]$lower_do_25, linetype="dotted", alpha = 0.5) + 
        geom_vline(xintercept=do[[i]]$upper_do_25, linetype="dotted", alpha = 0.5) 
   } else {
    do_plots[[i]] <- grid::grid.rect(gp = grid::gpar(col = "white"))
   }
 } else {
  do_plots[[i]] <- grid::grid.rect(gp = grid::gpar(col = "white"))
 }
}

@@

#### Calculate temperature curves
```{r}
td <- list()
temp_plots <- list()
for (i in seq_len(length(model_list))) {
 if(model_list[[i]]$model$convergence==0){
  td[[i]] <- fixed_density(model_list[[i]], predictor = "temp", fixed_params = num_params)
  if (length(td[[i]])>0) {
    td[[i]]$species <- species
    td[[i]]$age <- ifelse(grepl("imm", names(model_list[i])), "imm", "adult")
    td[[i]]$ssid <- unique(model_list[[i]]$data$ssid)
    td[[i]]$model <- names(model_list[i])
    td[[i]]$covs <- covs
   roots <- get_quadratic_roots(model_list[[i]], predictor = "temp", fixed_param = num_params, threshold = 0.5)
   td[[i]]$optimal_temp <- roots[["optimal"]]
   td[[i]]$lower_t_50 <- roots[["lower_threshold"]]
   td[[i]]$upper_t_50 <- roots[["upper_threshold"]]
   roots75 <- get_quadratic_roots(model_list[[i]], predictor = "temp", fixed_param = num_params, threshold = 0.75)
   td[[i]]$lower_t_75 <- roots75[["lower_threshold"]]
   td[[i]]$upper_t_75 <- roots75[["upper_threshold"]]
   roots25 <- get_quadratic_roots(model_list[[i]], predictor = "temp", fixed_param = num_params, threshold = 0.25)
   td[[i]]$lower_t_25 <- roots25[["lower_threshold"]]
   td[[i]]$upper_t_25 <- roots25[["upper_threshold"]]
   temp_plots[[i]] <- 
     plot_mountains(td[[i]], variable_label = "Temperature", xlimits = c(2, 10)) +
        ggtitle(paste(species, names(model_list[i]))) +
        geom_vline(xintercept=td[[i]]$optimal_t, size= 1.2, colour = "darkgrey") + 
        geom_vline(xintercept=td[[i]]$lower_t_50, linetype="longdash", alpha = 0.75) + 
        geom_vline(xintercept=td[[i]]$upper_t_50, linetype="longdash", alpha = 0.75) +
        geom_vline(xintercept=td[[i]]$lower_t_75, linetype="dotted", alpha = 0.5) + 
        geom_vline(xintercept=td[[i]]$upper_t_75, linetype="dotted", alpha = 0.5) +
        geom_vline(xintercept=td[[i]]$lower_t_25, linetype="dotted", alpha = 0.5) + 
        geom_vline(xintercept=td[[i]]$upper_t_25, linetype="dotted", alpha = 0.5)

@@

Save DO plots
```{r}
png(
  file = paste0("figs/", spp, "/do-fixed-", spp, covs, "-priors-", priors, ".png"),
  res = 600,
  units = "in",
  width = 8.5,
  height = 11
)
gridExtra::grid.arrange(
  grobs = do_plots,
  nrow = 4,
  top = grid::textGrob(paste(species))
)
dev.off()
```

Save Temperature plots
```{r}
png(
  file = paste0("figs/", spp, "/temp-fixed-", spp, covs, "-priors-", priors, ".png"),
  res = 600,
  units = "in",
  width = 8.5,
  height = 11
)
gridExtra::grid.arrange(
  grobs = temp_plots,
  nrow = 4,
  top = grid::textGrob(paste(species))
)
dev.off()
```

#### Save plots of raw densities vs model optimals 
```{r}
png(
  file = paste0("figs/", spp, "/check-optimals-", spp, covs, "-priors-", priors, ".png"),
  res = 600,
  units = "in",
  width = 8.5,
  height = 11
)
gridExtra::grid.arrange(grobs = c(raw_do_plots, raw_t_plots),
  nrow = 4,
  top = grid::textGrob(paste("Raw densities of", species, "with modeled optimals in vertical lines (if solid includes all surveys)"))
)
dev.off()
```

#### Save plots of time-varying depth from climate model
```{r}
png(
  file = paste0(
    "figs/", spp,
    "/depth-", spp, covs, "-priors-", priors, ".png"
  ),
  res = 600,
  units = "in",
  width = 8.5,
  height = 11
)
gridExtra::grid.arrange(
  grobs = depth_plots,
  nrow = 4,
  top = grid::textGrob(paste(species))
)
dev.off()
```
